Updates on the Exoplanet Orbit Database

### 2014-01-24 draft/ms.tex
Update

EOD

MICROLENSING, IMAGING, TIMING and ASTROMETRY

@@

MASS: we use mass-radius relation to get mass.

>>>>

EOD: Planets discovered by radial velocity and transit method are classified as EOD planets. They have robust orbital parameters such as PER, ECC, K, OM, and I.

MICROLENSING, IMAGING, TIMING and ASTROMETRY: We have added MICROLENS- ING, IMAGING, TIMING and ASTROMETRY fields for planets discovered by methods other than radial velocity and transit. These planets are categorized as ``Other Planets'' on exoplanets.org

@@

MASS: Previously, we only reported the minimum mass (MSINI) of the planets. We now report mass of the planet in the unit of Jupiter mass. If a planet is discovered by transit, the planet mass is given by the literature. However, if a planet is detected by radial velocity method, the minimum mass is given in which case we calculate the mass by dividing the minimum mass by the orbit inclination. MASS is set to MSINI if the orbital inclination is not given and the MASSREF is set to ``Set to MSINI; I unknown''

MASS: we use mass-radius relation to get mass. =>stellar mass?
